The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-02 albatros_paper.tex
HCC tweaked marion map figure, reorganized a bunch of text and added nominal writing assignments

% Define stuff here
\def\albatros{ALBATROS}

@@

\begin{abstract}
The low frequency radio astronomy has the highest potential in discovering the history of the Universe, this includes observations of the first stars and the mapping of dark ages. The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic (ALBATROS) is a new interferometric array. It consists of autonomous antenna stations that will map the low-frequency sky from Marion Island. One autonomous station was deployed in Marion Island in April 2019. The operating frequency range is \SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$. A two element inteferometer, the ALBATROS - Exploratory Gizmo on the Ground (ALBATROS-EGG) was deployed in Marion Island in April 2018. \\
\end{abstract}

@@

Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
Comprehensive reviews exist elsewhere ({\bf citation?}), and here, we
highlight only a few specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist only at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
    \caption{Marion Island huts which are
      potential stations for the ALBATROS. The ring-like pattern is
      appropriate for imaging and produces a FWHM synthesized beam of
      8' at 5 MHz.  {\bf add text here about which ones are huts vs current install sites}}
    \label{Fig:marion}
  \end{center}
\end{figure}

@@

The primary requirements that drive the design for a low-frequency
imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
ionospheric conditions.  As a benchmark, an interferometer operating
at 30~MHz requires order-of-magnitude baseline lengths of $\sim 1$~km
to achieve a resolution of $\sim 1$\degree.  This length scales
inversely with frequency, and therefore $\sim 10$-km lengths are
required at few-MHz frequencies in order to improve upon the
resolutions achieved to date.  {\bf More words here about RFI and
  ionosphere.}

The final array will consist of $\approx$ 10 antennas operating at
1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was
deployed in April 2018, the first autonomous station was deployed in
April 2019.

Marion Island is a research location managed by the South African
National Antarctic Programme (SANAP) and is located at
\ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern
Indian Ocean. It is $\approx$\SI{2000}{\kilo\metre} from the nearest
continental landmass which is also an approximate maximum distance
for meteor scattering. The island has an area of
\SI{290}{\kilo\metre\squared} and is only accessible once in April of
every year by means of the S. A. Agulhas vessel owned by the
Department of Environmental Affairs.

Marion Island huts which are potential stations for the ALBATROS have
a ring-like pattern which is appropriate for imaging and produces a
FWHM synthesized beam of 8' at 5 MHz as shown in
\autoref{Fig:10}. This beam is a notable advancement over existing
measurements to date.The ALBATROS main goal thus far will be to
attempt to map high resolutions at low frequencies which is crucial
before moving to measuring the dark ages.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/albatros_2elem/albatros_2elem.pdf}
    \caption{The two-element \albatros\ pathfinder on Marion Island.
      Two dual-polarization LWA antennas are separated by roughly
      110~m on an east--west baseline. Coaxial cables connect the
      antennas to an orange shipping container that houses the readout
      electronics and serves as our ``command module.''}
    \label{Fig:albatros2}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Schematic for the two-element \albatros\ pathfinder.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns ({\bf citation for FEE}), and 100-m
      coaxial cables connect the antennas to the back-end readout
      electronics, which are housed in a Faraday cage denoted by the
      dashed box.  Each of the four antenna outputs is passed to a
      second-stage electronics chain consisting of a bias tee,
      amplifier, and high- and low-pass filters.  The signals are
      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
      is programmed with firmware to perform a full cross-correlation
      of all four inputs.  A Raspberry Pi controls the SNAP board and
      also saves the computed spectra to an SD card.  Power to the
      system is provided by a bank of 12~V batteries and several
      regulated voltage outputs.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

The ALBATROS-EGG is a two element inteferometer which is making
exploratory measurements at a frequency range of \SI{1.2}{MHz}-
\SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in
\autoref{Fig:albatros2}. It was deployed in Marion Island in April
2018. Its schematic is shown in \autoref{Fig:albatros2_schem}. The
system uses the dual polarisation dipole like antennas which are
omidirectional patterned. The front end electonics (FEE) are
configured in a printed circuit board (PCB) which makes it easy for
them to be mounted on the supporting structure of the antennas. From
the FEE PCB, a coaxial cable sends the signal through to the bias tee
which extracts both the RF and the DC without any degradation.

The high pass and the low pass filter rejects the low frequency
signals and high frequency signals respectively. The signal is then
amplified by a $\approx$20 dB amplifier which then send the amplified
signals to the Smart Network ADC Processor (SNAP) board which does the
readouts and does a series of processing step. The raspberry pi
interacts with the SNAP board for data storage.

The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky. Since these experiments are exploratory, they are taking steps towards achieving the future objective of probing the Dark Ages.The ALBATROS stations (huts) will be separated by baselines of \SI{\approx {20}}{km} as shown in \autoref{Fig:Marion}. The two-element interferomentric pathfinder is not yet operating autonomously, it uses the direct cross correlation technique whereas the yet to be ALBATROS will write the lowest 10 - 20 MHz baseband to disk then gets correlated afterwards. One ALBATROS fully autonomous station was deployed in Marion Island in April 2019 as shown in \autoref{Fig:autonomous}. \\

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
		\caption{Analog signal chain block diagram for the newly deployed autonomous station the ALBATROS}
		\label{Fig:Signal Chain}
	\end{center}
\end{figure}

\subsection{Antenna}	
The system uses the dual polarisation dipole like antennas which are omidirectionally patterned. The dipole like antennas are of high preference for this project because they are relatively simple and they are omnidirectionally patterned \cite{Memo28}.

\subsection{Front End Electronics (FEE)}
All the front end components were incorporated for in a double sided printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the block diagram is shown in \autoref{Fig:Balun Schematic}. The Monolithic Microwave Integrated Circuits (MMICs) is the used design for the PCB. One side of the PCB is populated with components and the other side is a solid copper ground plane aperiodically stitched to the grounded copper on the side populated with components. The receiver system is made up of the active balun, filter and the gain stage that connects to the \SI{100}{\metre} coaxial cable which is connected to the back end \cite{2012PASP..124.1090H}.\\ 
The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is introduced to the dipole by the active balun. The signal is then fed through an amplifier which amplifies it by \SI{+24}{\decibel} of gain. The balanced signal is then converted to unbalanced through a 180 \degree hybrid coupler. The band pass filter (BPF) receives the single ended signal in order for it to reject all the frequencies which are not within the range of interest. The signal gets fed to a second amplifier which again amplies it by \SI{+24}{\decibel} of gain and the output impedance of the FEE is matched to a \SI{50}{\ohm} coaxial cable. The bias tee is responsible for providing power to the FEE and extracts the RF signal by the use of the coaxial cable. This unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$ \SI{2.9}{\decibel} \cite{Memo35}.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
		\label{Fig:Balun}
	\end{center}
\end{figure}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
		\label{Fig:Balun Schematic}
	\end{center}
\end{figure}

\subsection{Back End Electronics}	
The back end electronics consists of the bias tee, high pass filter (HPF), low pass filter (LPF) and the Smart Network ADC Processor (SNAP) board. \\

\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an insertion loss of \SI{0.16}{\decibel} at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\

\textbf{HPF} - The HPF rejects any signals with low frequencies and allow through signals with high frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}. The HPF used is the ZFHP-1R2+ Mini Circuits device which operates between  \SI{1.2}{MHz} - \SI{800}{MHz}. It has a nominal insertion loss of $\approx$ \SI{0.2}{\decibel} at centre frequency of  \SI{\approx10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.\\

\textbf{LPF} - The LPF rejects all signals with high frequencies and allows all signals with low frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}. The LPF used is the SLP-90+ Mini Circuits device which operates between \SI{1}{MHz} - \SI{400}{MHz}. It has a nominal insertion loss of $\approx$ \SI{0.14}{\decibel} at the centre frequency of  \SI{\approx 10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.\\

\textbf{Amplifier} - The amplifier at the backend amplifies the signal which is sent through to the snapboard by the gain of \SI{+20}{\decibel}. The amplifier used is the Mini Circuits device ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} - \SI{6}{GHz}. It has a noise figure of $\approx$ \SI{3.6}{\decibel} at its lowest operating frequency of \SI{\approx 50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.\\

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The  SNAP board samples the signals it receives by 250 Msampl/s using internal ADCs where the signal of the clock is from the Valon 5007 frerquency synthesizer module. This creates a frequency range between \SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board interacts with a raspberry pi and that is where the data is saved.\\

\subsection{Solar Power Supply System}
The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days. From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down. Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period. Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\

@@

\section{Pathfinder Installations and Preliminary Observations}

 \subsection{Experiments}
 The ALBATROS-EGG shown in \autoref{Fig:ALBATROS-EGG} was installed on the PRI\textsuperscript{z}M \cite{2019JAI.....850004P} site which is located at \ang{46;53;13}S, \ang{37;49;10.7}E and the first ALBATROS station shown in \autoref{Fig:autonomous} is located \ang{46;52.205;}S, \ang{37;50.612;}E.\\

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
			\caption{}
			\label{Fig:autonomous}
		\end{center}
	\end{figure}

 \subsection{Preliminary Observations}

>>>>

% Define stuff here
\def\albatros{ALBATROS}
\def\prizm{PRI$^{\rm Z}$M}

@@

\begin{abstract}
\textcolor{red}{\bf text to be overhauled later...} \\
The low frequency radio astronomy has the highest potential in
discovering the history of the Universe, this includes observations
of the first stars and the mapping of dark ages. The Array of Long
Baseline Antennas for Taking Radio Observations from the
Sub-Antarctic (ALBATROS) is a new interferometric array. It consists
of autonomous antenna stations that will map the low-frequency sky
from Marion Island. One autonomous station was deployed in Marion
Island in April 2019. The operating frequency range is
\SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$. A
two element pathfinder was deployed in Marion Island in April
2018.
\end{abstract}

@@

Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
Comprehensive reviews exist elsewhere (\textcolor{red}{\bf find a good
  reference}), and here, we highlight only a few specific examples.
At the very lowest frequencies, the state of the art among
ground-based measurements dates from the 1950s, when Reber and Ellis
caught brief glimpses of the $2.1$~MHz sky at $\sim
5$\degree\ resolution, using an array of 192~dipoles~\citep{reber,
  article, 1988A&A...195..372W}.  A few space-based missions have also
performed measurements at similarly low frequency ranges; for example,
the Radio Astronomy Explorer-2 operated at \SIrange{0.025}{13}{\MHz}
with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist only at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.

\textcolor{red}{\bf More text about the science case, including
  Galactic astrophysics (Jon? Jeff?)}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
    \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
      are currently installed at the \prizm\ site and at the hydro
      shack.  The black markers denote the eight coastal huts, which
      will be used for future \albatros\ antenna installations.  The
      white markers denote other available infrastructure points that
      will not be used for antennas.  \textcolor{red}{\bf Add new
        synthesized beam figure (Jon)}}
    \label{Fig:marion}
  \end{center}
\end{figure}

@@

The primary requirements that drive the design for a low-frequency
imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
ionospheric conditions.  As a benchmark, an interferometer operating
at 30~MHz requires order-of-magnitude baseline lengths of $\sim 1$~km
to achieve a resolution of $\sim 1$\degree.  This length scales
inversely with frequency, and therefore $\sim 10$-km lengths are
required at few-MHz frequencies in order to improve upon the
resolutions achieved to date.  The experiment installation site must
be remote to keep RFI to a minimum, and polar or near-polar latitiudes
generally have lower ionospheric plasma frequency cutoffs.
\textcolor{red}{\bf Add more ionosphere text here, plus IRI simulation
  fig/numbers (Jon)}

Marion Island is a research base that is located in the southern
Indian Ocean at \ang{46;54;45}S, \ang{37;44;37}E and is operated by
the South African National Antarctic Programme.  The island lies
roughly \SI{2000}{\kilo\metre} from the nearest continental landmasses
and has an exceptionally quiet RFI
environment~\citep{2019JAI.....850004P}.  As illustrated in
\autoref{Fig:marion}, Marion has an area of 335~km$^2$ and can
therefore support antenna installations with $>10$-km baseline
lengths.  The main Marion base is located on the northeast side of the
island, and there are eight rest huts along the coast (Cape Davis,
Grey-headed, Kildalkey, Mixed Pickle, Repettos, Rooks, Swartkops,
Watertunnel) and one in the interior (Katedraal) that can serve as
existing infrastructure points for antenna installations.  The planned
\albatros\ installation sites include the coastal huts, but exclude
the main base and Katedraal for RFI and accessibility reasons,
respectively.  \autoref{Fig:marion} also shows the locations of the
\albatros\ pathfinder antennas that are currently installed at the
\prizm\ site and at the hydro shack.

Using the eight coastal huts, the \prizm\ site, and the hydro shack as
the nominal \albatros\ installation locations, the computed
synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
of magnitude improvement in resolution over other existing
measurements.  One of the challenges in constructing an interferometer
array on Marion Island is that the rugged terrain precludes the
possibility of directly cabling and correlating antennas across large
distances.  The final \albatros\ antenna stations will therefore
operate {\it autonomously}, recording baseband data over extended
periods of time for subsequent offline correlation.  We have conducted
two enginering runs: 1) a two-element, directly correlated pathfinder
to qualitatively understand the sky signal, and 2) a single station to
test the readout and power handling technology that are required for
autonomous operation.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/albatros_2elem/albatros_2elem.pdf}
    \caption{The two-element, directly correlated
      \albatros\ pathfinder installed at the \prizm\ site.  Two
      dual-polarization antennas are separated by roughly 110~m on an
      east--west baseline. Coaxial cables connect the antennas to a
      shipping container that houses the readout electronics and
      serves as the ``command module.'' \textcolor{red}{\bf Add FEE
        and backend sub-pics here? (HCC)}}
    \label{Fig:albatros2}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Schematic for the two-element \albatros\ pathfinder.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\textcolor{red}{\bf citation for FEE}),
      and 100-m coaxial cables connect the antennas to the back-end
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of a bias tee,
      amplifier, and high- and low-pass filters.  The signals are
      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
      is programmed with firmware to perform a full cross-correlation
      of all four inputs.  A Raspberry Pi controls the SNAP board and
      also saves the computed spectra to an SD card.  Power to the
      system is provided by a bank of 12~V batteries and several
      regulated voltage outputs.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

The first exploratory \albatros\ measurements were conducted with a
two-element pathfinder that employed direct correlation (without
autonomous operation).  \autoref{Fig:albatros2} illustrates this
pathfinder, which was installed at the \prizm\ site (\ang{46;53;13}S,
\ang{37;49;10.7}E) in April 2018.  The system schematic is illustrated
in \autoref{Fig:albatros2_schem}, and each of the subsystems is
described in detail below.

\subsection{Antenna}	
We employ two dual-polarization Long Wavelength Array (LWA) dipole
antennas~\citep{Memo28}.  The LWA antennas have a long development
history, are well characterized, and are simple to install and
physically robust.  The antennas form an east--west baseline with a
separation of \SI{110}{m}, and the polarizations are aligned with the
cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
are installed on the ground below the antennas.
% do we want/need to say anything about the omnidirectional primary beam?

\textcolor{red}{\bf ALL TEXT BELOW HERE NEEDS WORK}

\subsection{Front-end active balun}
\textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\
All the front end components were incorporated for in a double sided
printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
block diagram is shown in \autoref{Fig:Balun Schematic}. The
Monolithic Microwave Integrated Circuits (MMICs) is the used design
for the PCB. One side of the PCB is populated with components and the
other side is a solid copper ground plane aperiodically stitched to
the grounded copper on the side populated with components. The
receiver system is made up of the active balun, filter and the gain
stage that connects to the \SI{100}{\metre} coaxial cable which is
connected to the back end \cite{2012PASP..124.1090H}.

The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is
introduced to the dipole by the active balun. The signal is then fed
through an amplifier which amplifies it by \SI{+24}{\decibel} of
gain. The balanced signal is then converted to unbalanced through a
180 \degree hybrid coupler. The band pass filter (BPF) receives the
single ended signal in order for it to reject all the frequencies
which are not within the range of interest. The signal gets fed to a
second amplifier which again amplies it by \SI{+24}{\decibel} of gain
and the output impedance of the FEE is matched to a \SI{50}{\ohm}
coaxial cable. The bias tee is responsible for providing power to the
FEE and extracts the RF signal by the use of the coaxial cable. This
unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall
noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$
\SI{2.9}{\decibel} \cite{Memo35}.

\subsection{Back End Electronics}
\textcolor{red}{\bf Nivek, HCC?} \\
The back end electronics consists of the bias tee, high pass filter
(HPF), low pass filter (LPF) and the Smart Network ADC Processor
(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.

\textbf{Bias Tee} - It is used to extract the RF signal from a
\SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation
of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx
  3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz}
respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The
bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+
which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an
insertion loss of \SI{0.16}{\decibel} at centre frequency of
\SI{\approx 10}{MHz} as per the
datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.

\textbf{HPF} - The HPF rejects any signals with low frequencies and
allow through signals with high
frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}. The
HPF used is the ZFHP-1R2+ Mini Circuits device which operates between
\SI{1.2}{MHz} - \SI{800}{MHz}. It has a nominal insertion loss of
$\approx$ \SI{0.2}{\decibel} at centre frequency of
\SI{\approx10}{MHz} as per the
datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.

\textbf{LPF} - The LPF rejects all signals with high frequencies and
allows all signals with low
frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}. The
LPF used is the SLP-90+ Mini Circuits device which operates between
\SI{1}{MHz} - \SI{400}{MHz}. It has a nominal insertion loss of
$\approx$ \SI{0.14}{\decibel} at the centre frequency of \SI{\approx
  10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.

\textbf{Amplifier} - The amplifier at the backend amplifies the signal
which is sent through to the snapboard by the gain of
\SI{+20}{\decibel}. The amplifier used is the Mini Circuits device
ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} -
\SI{6}{GHz}. It has a noise figure of $\approx$ \SI{3.6}{\decibel} at
its lowest operating frequency of \SI{\approx
  50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
SNAP board samples the signals it receives by 250 Msampl/s using
internal ADCs where the signal of the clock is from the Valon 5007
frerquency synthesizer module. This creates a frequency range between
\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
interacts with a raspberry pi and that is where the data is saved.

\subsection{Power}
\textcolor{red}{\bf Tankiso?} \\
Text here about generators.

\section{Single autonomous station pathfinder}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
    \caption{Schematic for single autonomous station pathfinder.
      \textcolor{red}{\bf Update this figure and make it similar to
        the two-element schematic.  Tankiso, Nivek, HCC?}}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}

\textcolor{red}{\bf Nivek?} \\

A single, autonomous station pathfinder was installed at the hydro
shack (\ang{46;52.205;}S, \ang{37;50.612;}E) in April 2019.

The final project (ALBATROS) will consist of autonomous antenna
stations that will map the low frequency sky. Since these experiments
are exploratory, they are taking steps towards achieving the future
objective of probing the Dark Ages.The ALBATROS stations (huts) will
be separated by baselines of \SI{\approx {20}}{km} as shown in
\autoref{Fig:Marion}. The two-element interferomentric pathfinder is
not yet operating autonomously, it uses the direct cross correlation
technique whereas the yet to be ALBATROS will write the lowest 10 - 20
MHz baseband to disk then gets correlated afterwards. One ALBATROS
fully autonomous station was deployed in Marion Island in April 2019
as shown in \autoref{Fig:autonomous}.

@@

% HCC: we probably don't need these figures below, or we can
% incorporate them as subfigs into other places

% \begin{figure}[h]
% 	\begin{center}
% 		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
% 		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
% 		\label{Fig:Balun}
% 	\end{center}
% \end{figure}
% 
% \begin{figure}[h]
% 	\begin{center}
% 		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
% 		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
% 		\label{Fig:Balun Schematic}
% 	\end{center}
% \end{figure}

\subsection{Solar power system}
\textcolor{red}{\bf Nivek, Tankiso, Eamon?} \\
The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days. From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down. Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period. Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\

@@

\section{Preliminary observations}

\textcolor{red}{\bf NEED UPDATED AND NEW PLOTS, NEED VOLUNTEERS FOR THIS:
  \begin{itemize}
    \item{Improved waterfall plots from 2-element pathfinder}
    \item{Plot showing that the solar power works (sort of)}
    \item{Some sort of...data...plot for the autonomous station.  Can
      we say anything about baseband performance?}
  \end{itemize}
}
